\P\textit{This Order may be used as a separate Service: or it may be said at the opening of Evening Service, instead of the Order there appointed, down to the} Reading of the Holy Scriptures; \textit{in which case it may be preceded by a suitable Hymn.} \\

\noindent\P\textit{Let all stand while the Minister reads the} \textsc{Sentences,} \textit{the People answering him.} \\

% Fill this in     

{\centering \P\textit{Then the Minister shall say,} \\ Let us pray. \par}
\vspace{1ex}
\noindent\P\textit{Let the People reverently bow down while he leads them in}

\section*{The Invocation}

\lettrine{M}{erciful} God, we beseech Thee to cast Thy bright beams of light into our hearts, that we may discern the spiritual laws of Thy kingdom, and graciously incline us to a true obedience that we may not only hear, but also receive, these heavenly blessings of our Lord Jesus Christ.
\textit{Amen.} \\

\noindent\P\textit{Then the Minister shall read} \textsc{The Beatitudes} \textit{of the Lord Jesus; and the People, still bowing down, shall, after every Beatitude, humbly ask God that it may be fulfilled in their hearts.} \\

\noindent\lettrine{B}{lessed} are the poor in spirit: for theirs is the kingdom of heaven.

\textit{Lord, be gracious unto us, and help us to obtain this blessing.}   

Blessed are the meek: for they shall inherit the earth.

\textit{Lord, be gracious unto us, and help us to obtain this blessing.}   

Blessed are they which do hunger and thirst after righteousness: for they shall be filled.

\textit{Lord, be gracious unto us, and help us to obtain this blessing.}   

Blessed are the merciful: for they shall obtain mercy.

\textit{Lord, be gracious unto us, and help us to obtain this blessing.}   

Blessed are the pure in heart: for they shall see God.

\textit{Lord, be gracious unto us, and help us to obtain this blessing.}   

Blessed are the pure in heart: for they shall be called the children of God.

\textit{Lord, be gracious unto us, and help us to obtain this blessing.}   

Blessed are they which are persecuted for righteousness' sake: for theirs is the kingdom of heaven.

\textit{Grant unto us Thy Holy Spirit, O God, and enable us to obtain all these blessings, through Jesus Christ our Lord.} \\

\noindent\P\textit{After a short pause, let the Minister continue in Prayer, using, if he will, the following, or other fitting words.} \\

\noindent\lettrine{G}{lory} be to Thee, O Christ, who hast opened the kingdom of heaven unto the poor in spirit, and given power to them that believe in Thee to become the sons of God.
Deliver us, O Lord, in Thy great mercy, from all the secret sins that hinder us from true blessedness.
Strengthen us to keep Thy counsels of perfection, and to walk in the way of Thy commandments.
And grant unto us that peace which the world can neither give nor take away, that at the last we may come unto Thee in glory, O Thou most blessed Lord Jesus, our only Saviour.  
\textit{Amen.} \\

\noindent\lettrine{N}{ow} unto Him that is able to do exceeding abundantly above all that we ask or think, according to the power that worketh in us; unto Him be glory and dominion in the Church by Jesus Christ, throughout all ages, world without end.
\textit{Amen.} 
