\P \textit{This service is intended for the use of any company of Christians, gathered together to worship God, on land or at sea, where there are no regular Church Ordinances, or where a Minister of the Gospel is not present.} \\

\noindent\P\textit{If it be desired, the Service may begin with the Singing of a Hymn; after which the Leader, standing, may read one or more of the following} \textsc{Sentences} \textit{taken from the} \textsc{Holy Scriptures.}   

\section*{Sentences}
\section*{\normalsize Morning}

\lettrine{T}{he} Lord is nigh unto all them that call upon Him, to all that call upon Him in truth.
He will fulfil the desires of them that fear Him; He also will hear their cry, and will save them. \\

Our help is in the Name of the Lord, who made heaven and earth. \\

Where two or more are gathered in My Name, saith the Lord Jesus, there am I in the midst of them. \\

This is the confidence that we have in Him, that, if we ask anything according to His will, He heareth us.

Having these promises, let us draw near to the throne of grace with true hearts, in full assurance of faith. \\

My voice shalt Thou hear in the morning, O Lord; in the morning will I direct my prayer unto Thee, and will look up.

\section*{\normalsize Evening}

\lettrine{H}{e} that dwelleth in the secret place of the Most High shall abide under the shadow of the Almighty. \\

Lord, I cry unto Thee: make haste unto me; give ear unto my voice, when I cry unto Thee.

Let my prayer be set before Thee as incense; and the lifting up of my hands as the evening sacrifice. \\

I will say of the Lord, He is my refuge, and my fortress: my God; in Him will I trust. \\

Return unto thy rest, O my soul; for the Lord hath dealt bountifully with thee.

Abide with us; for it is toward evening, and the day is far spent.

{\centering \P\textit{Then shall he say,} \\ Let us pray. \par} 
\vspace{2ex}
\noindent\P\textit{Let all the company bow down, following the Prayer in their hearts, and, if they so desire, joining audibly in the} \textsc{Confession of Sins} \textit{and the} \textsc{Lord's Prayer.}    

\section*{Prayers}

\lettrine{A}{lmighty} God, unto whom all hearts are open, all desires known, and from whom no secrets are hid; Cleanse the thoughts of our hearts by the inspiration of Thy Holy Spirit, that we may perfectly love Thee, and worthily magnify Thy holy Name; through Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{M}{ost} holy and merciful Father; We acknowledge and confess in Thy Presence: Our sinful nature prone to evil and slothful in good; And all our shortcomings and offense against Thee.
Thou alone knowest how often we have sinned: In wandering from Thy ways; in wasting Thy gifts; In forgetting Thy love.
But Thou, O Lord, have pity upon us; Who are ashamed and sorry for all wherein we have displeased Thee.
Teach us to hate our errors; Cleanse us from our secret faults; and forgive our sins; For the sake of Thy dear Son our Saviour.
And O most holy and loving Father: Send Thy purifying grace into our hearts, we beseech Thee; That we may henceforth live in Thy light and walk in Thy ways; According to the commandments of Jesus Christ our Lord.
\textit{Amen.} \\

\lettrine{O}{ur} Father which art in heaven, Hallowed be Thy Name.
Thy kingdom come.
Thy will be done in earth, As it is in heaven.
Give us this day our daily bread.
And forgive us our debts, As we forgive our debtors.
And lead us not into temptation, But deliver us from evil:
For Thine is the kingdom, and the power, and the glory, for ever.
Amen.

\section*{The Psalter}

\P \textit{A portion of the} \textsc{Psalter} \textit{may then be read by the Leader, or recited responsively, closing with this} \textsc{Ascription.} \\

Glory be to the Father, and to the Son, and to the Holy Ghost; \par
As it was in the beginning, is now, and ever shall be: world without end. Amen. \\

{\centering \P \textit{Let all the company, standing, repeat together} \par} 

\section*{The Apostles' Creed}

\lettrine{I}{ believe} in God the Father Almighty, Maker of heaven and earth: \par
And in Jesus Christ His only Son, our Lord; Who was conceived by the Holy Ghost, Born of the Virgin Mary, Suffered under Pontius Pilate, Was crucified, dead, and buried; [He descended into hell;\footnote{Or, \textit{He continued in the state of the dead, and under the power of death, until the third day.}}]
The third day He rose again from the dead; He ascended into heaven, And sitteth on the right hand of God the Father Almighty; From thence He shall come to judge the quick and the dead. \par
I believe in the Holy Ghost; The Holy Catholic Church; The Communion of Saints; The Forgiveness of sins; The Resurrection of the body; and the Life everlasting. Amen.

\section*{The Reading of the Holy Scriptures}

\P \textit{The Leader shall choose and read an appropriate lesson, or lessons, from the Bible, saying before he reads,} Let us listen reverently to the Holy Scripture, as it is written in the -- chapter of --; \textit{and after the reading he shall say,} May God bless, to all our hearts, the reading of His Word.

\section*{A Hymn}  

\P \textit{If it be convenient the company may then sing a Hymn; and after this, if it be desired, the Leader may read a Sermon, or a brief passage from some Christian book; or a word of exhortation and counsel may be spoken by the Leader or some other member of the company.
If this is done, let another Hymn be sung before the closing Prayers.
The Leader may choose from the following such as are appropriate; and, the company bowing, he shall say,} \\

{\centering Let us pray. \par}

\section*{Prayers}

\section*{Thanksgiving} 

\lettrine{O}{ God,} by whose hand all living things were made, and by whose blessing they are nourished and sustained; We give Thee hearty thanks for all the bounties of Thy providence, wherewith Thou hast enriched our life; and we humbly pray that, enjoying Thy gifts in contentment, we may be enabled by Thy grace to use them to Thy praise.
Especially we thank Thee for Thy great love in sending Thy Son to be the Saviour of the world and in calling us out of our sins into fellowship with Him; and we beseech Thee to grant us always Thy Holy Spirit, through whom we may grow continually in thankfuless toward Thee, as also into the likeness of Thy Son Jesus Christ our Lord.
\textit{Amen.}

\section*{Supplication}

\lettrine{O}{ God,} most holy, wise, and powerful Preserver and Governor of all Thy creatures and all their actions; Keep us this day in health of body and soundness of mind, in purity of heart and cheerfulness of spirit, in contentment with our lot and charity with our neighbor; and further all our lawful undertakings with Thy blessing.
In our labour strengthen us: in our pleasure purify us: in our difficulties direct us: in our perils defend us: in our troubles comfort us: and supply all our needs, according to the riches of Thy grace in Christ Jesus our Lord.
\textit{Amen.}

\section*{A Traveller's Prayer}  

\lettrine{L}{ord} God omnipotent, who reignest in the heavens and on the earth; We implore Thy guidance and protection for all our journeyings.
Against all perils be Thou our strong defense, and in far regions be Thou our faithful friend; keep us in health and heart; prosper the ends of our adventure, and make the way of our going and of our returning both safe and happy; and so direct the steps of all Thy pilgrims through this world, that we shall finally arrive in the better country, even the heavenly, with Jesus Christ our Lord.
\textit{Amen.}

\section*{A Prayer at Sea}

\lettrine{O}{ Eternal} Lord God, who alone spreadest out the heavens, and rulest the raging of the sea; We commend ourselves to Thine almighty protection on the great deep.
Guard us, we beseech Thee, from the dangers of the sea, from sickness, from the violence of enemies, from every evil; and conduct us in safety to our desired haven, with a grateful sense of Thy mercies; through Jesus Christ our Lord.
\textit{Amen.}

\section*{A Prayer for Friends and Kindred}

 \lettrine{O}{ Lord,} our heavenly Father, bless and keep, we pray Thee, our kindred, friends, and benefactors, and graciously watch between them and us, while we are absent from one another, that in due time we may meet again to praise Thee, and hereafter dwell together in heavenly mansions; through Christ our Lord.
\textit{Amen.}

\section*{A General Intercession}

\lettrine{O}{ God,} the Creator and Preserver of all mankind, we humbly beseech Thee for all sorts and conditions of men; that Thou wouldest be pleased to make Thy ways known unto them, Thy saving health unto all nations.
More especially, we pray for Thy holy Church universal; that it may be so guided and governed by Thy good Spirit, that all who profess and call themselves Christians may be led into the way of truth, and hold the faith in unity of spirit, in the bond of peace, and in righteousness of life.
Finally, we commend to Thy fatherly goodness all those who are any ways afflicted, or distressed, in mind, body, or estate; that it may please Thee to comfort and relieve them, according to their several necessities; giving them patience under their sufferings, and a happy issue out of all their afflictions.
And this we beg for Jesus Christ's sake.
\textit{Amen.} 

\section*{A General Prayer in the Morning}

\lettrine{A}{lmighty} God, our Father and Preserver; We give Thee thanks that of Thy goodness Thou hast watched over us the past night, and brought us to a new day: and we beseech Thee to strengthen and guard us by Thy Spirit, that we may spend it wholly in Thy service and to Thy glory, looking for all prosperity to Thy blessing, and seeking only those things which are well-pieasiug in Thy sight.
Enable us, O Lord, while we labour for the life that now is, ever to have regard unto that heavenly life which Thou hast promised Thy children.
Defend us in soul and body from all harm.
And seeing it is a small thing to have begun well, except we also persevere, take us, O Lord, into Thy good keeping this day and all our days: continue and increase Thy grace within us, until we shall be perfectly united in the glory of Thy Son.
Show Thy loving-kindness unto all men and women and little children, according to the need of every living soul, especially unto those whom we love, and those who are in any kind of trouble or distress, whom we now remember silently before Thee: [\textit{here let there be a moment of prayer in silence:}] Protect our country and prosper Thy Church: Bless all who do good in the world, and restrain and convert all who do evil.
And finally, be pleased to cast out of Thy remembrance all our past offenses, forgiving them in Thy boundless mercy and purifying our hearts that we may lead a better life; through Jesus Christ our Lord.
\textit{Amen.}

\section*{A General Prayer in the Evening}

\lettrine{O}{ God} most merciful, Light eternal in the darkness shining, by whom the night of sin and the blindness of our hearts are driven away: Since Thou hast appointed the day for labour and the night for rest; grant unto us, we beseech Thee, that our bodies may repose in peace and quietness, that afterward they may be able to endure the toil which Thou hast laid upon us in Thy service: Temper our sleep that it be not disorderly, and keep us spotless both in body and in soul, that our very rest may be to Thy glory, renewing the strength of our hearts and our joy in Thee: Enlighten the eyes of our understanding that we may not sleep in death, but obtain deliverance, through faith and hope, from all fear of this misery: Defend us against all assaults of our enemies, and take us into Thy holy protection.
And although we have not passed this day without greatly sinning against Thee, we beseech Thee to hide our sins with Thy mercy, as Thou coverest all things on earth with the darkness of the night, that they may be blotted out from Thy remembrance, and we may abide in Thy Presence and Thy favour, both now and for evermore.
Relieve and comfort, with Thy fatherly goodness, all who are afflicted or distressed in mind, body, or estate: Protect and prosper, with Thine almighty power, our country and our rulers, the whole Church of Christ on earth, our home, and all that we hold dear and sacred: Be pleased to guard and help those whom we silently remem- ber before Thee: [\textit{here let there he a moment of prayer in silence:}] Bless us and keep us, watch over us and save us, O God in whom we trust ; through Jesus Christ our Lord.
\textit{Amen.} \\

\lettrine{L}{ighten} our darkness, we beseech Thee, O Lord; and by Thy great mercy defend us from all perils and dangers of this night; for the love of Thy only Son, our Saviour, Jesus Christ.
\textit{Amen.} 

\section*{A Prayer of St. Chrysostom}  

\lettrine{A}{lmighty} God, who hast given us grace at this time with one accord to make our common supplications unto Thee; and dost promise that when two or three are gather together in Thy Name Thou wilt grant their requests: Fulfil now, O Lord, the desires and petitions of Thy servants, as may be most expedient for them; granting us in this world knowledge of Thy truth, and in the world to come life everlasting.
\textit{Amen.} \\

\noindent\P\textit{All the company still bowing down, the Leader may close the Service with this}

\section*{Ascription}

\lettrine{N}{ow} unto Him that is able to keep us from falling, and to present us faultless before the presence of His glory with exceeding joy; to the only wise God our Saviour, be glory and majesty, dominion and power, both now and ever.
\textit{Amen.} 
