\P\textit{One of the first three Canticles may, if so desired, be sung at the beginning of Morning Service as the} \textsc{Opening Hymn.}

\section*{I.}
\section*{Venite, Exultemus Domino.}

\lettrine{O}{ come,} let us sing unto the Lord: let us heartily rejoice in the strength of our salvation.

Let us come before His Presence with thanksgiving: and show ourselves glad in Him with psalms.

For the Lord is a great God: and a great King above all gods.

In His hand are all the corners of the earth: and the strength of the hills is His also.

The sea is His, and He made it: and His hands prepared the dry land.

O come, let us worship and fall down: and kneel before the Lord our Maker.

For He is the Lord our God: and we are the people of His pasture, and the sheep of His hand.

O worship the Lord in the beauty of holiness: let the whole earth stand in awe of Him.

For He cometh, for He cometh to judge the earth: and with righteousness to judge the world, and the people with His truth.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen. 

\section*{II.}
\section*{Jubilate Deo.}

\lettrine{O}{ be} joyful in the Lord, all ye lands: serve the Lord with gladness, and come before His Presence with a song. 

Be ye sure that the Lord He is God; it is He that hath made us, and not we ourselves: we are His people, and the sheep of His pasture.

O go your way into His gates with thanksgiving, and into His courts with praise: be thankful unto Him, and speak good of His Name.

For the Lord is gracious, His mercy is everlasting: and His truth endureth from generation to generation.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen.

\section*{III.}
\section*{Letatus Sum.}

\lettrine{I}{ was} glad when they said unto me: Let us go into the house of the Lord.

Our feet shall stand within thy gates: O Jerusalem.

Jerusalem is builded as a city: that is compact together:

Whither the tribes go up, the tribes of the Lord: unto the testimony of Israel, to give thanks unto the Name of the Lord.

For there are set thrones of judgment: the thrones of the house of David.

Pray for the peace of Jerusalem: they shall prosper that love thee.

Peace be within thy walls: and prosperity within thy palaces.

For my brethren and companions' sakes: I will now say, Peace be within thee.

Because of the house of the Lord our God: I will seek thy good.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen. 

\section*{IV.}
\section*{Te Deum Laudamus.}

\lettrine{W}{e} praise Thee, O God: we acknowledge Thee to be the Lord.

All the earth doth worship Thee: the Father everlasting.

To Thee all Angels cry aloud: the Heavens, and all the Powers therein;

To Thee Cherubim and Seraphim: continually do cry,

Holy, Holy, Holy: Lord God of Sabaoth;

Heaven and earth are full of the Majesty: of Thy glory.

The glorious company of the Apostles: praise Thee.

The goodly fellowship of the Prophets: praise Thee.

The noble army of Martyrs: praise Thee.

The holy Church throughoutall the world: doth acknowledge Thee;

The Father: of an infinite Majesty;

Thine adorable, true: and only Son;

Also the Holy Ghost: the Comforter.

Thou art the King of Glory: O Christ.

Thou art the everlasting Son: of the Father.

When Thou tookest upon Thee to deliver man: Thou didst humble Thyself to be born of a Virgin.

When Thou hadst overcome the sharpness of death: Thou didst open the Kingdom of Heaven to all believers.

Thou sittest at the right hand of God: in the glory of the Father.

We believe that Thou shalt come: to be our Judge.

We therefore pray Thee, help Thy servants: whom Thou hast redeemed with Thy precious blood.

Make them to be numbered with Thy Saints: in glory everlasting.

O Lord, save Thy people: and bless Thine heritage.

Govern them: and lift them up for ever.

Day by day: we magnify Thee;

And we worship Thy Name: ever, world without end.

Vouchsafe, O Lord: to keep us this day without sin.

O Lord, have mercy upon us: have mercy upon us.

O Lord let Thy mercy be upon us: as our trust is in Thee.

O Lord, in Thee have I trusted: let me never be con-
founded. 

\section*{V.}
\section*{Gloria in Excelsis}

\lettrine{G}{lory} be to God on high: and on earth peace, good will towards men.

We praise Thee, we bless Thee, we worship Thee: we glorify Thee, we give thanks to Thee for Thy great glory.

O Lord God, heavenly King: God the Father Almighty.

O Lord, the only-begotten Son, Jesus Christ: O Lord God, Lamb of God, Son of the Father,

That takest away the sins of the world: have mercy upon us.

Thou that takest away the sins of the world: receive our prayer.

Thou that sittest at the right hand of God the Father: have mercy upon us.

For Thou only art holy: Thou only art the Lord.

Thou only, O Christ, with the Holy Ghost: art most high in the glory of God the Father. Amen. 

\section*{VI.}
\section*{Benedicte, Omnia Opera Domini.}

\lettrine{O}{ ALL} ye Works of the Lord, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Angels of the Lord, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Heavens, bless ye the Lord : praise Him, and magnify Him for ever.

O ye Waters that be above the firmament, bless ye the Lord: praise Him, and magnify Him for ever.

O all ye Powers of the Lord, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Sun and Moon, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Stars of heaven, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Showers and Dew, bless ye the Lord: praise Him, and magnify Him for ever. 

O ye Winds of God, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Fire and Heat, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Winter and Summer, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Dews and Frosts, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Frost and Cold, bless ye the Lord : praise Him, and magnify Him for ever.

O ye Ice and Snow, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Nights and Days, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Light and Darkness, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Lightnings and Clouds, bless ye the Lord: praise Him, and magnify Him for ever..

O let the Earth bless the Lord: yea, let it praise Him, and magnify Him for ever.

O ye Mountains and Hills, bless ye the Lord: praise Him, and magnify Him for ever.

O all ye Green Things upon the earth, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Wells, bless ye the Lord : praise Him, and magnify Him for ever.

O ye Seas and Floods, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Whales, and all that move in the waters, bless ye the Lord : praise Him, and magnify Him for ever.

O all ye Fowls of the air, bless ye the Lord : praise Him, and magnify Him for ever.

O all ye Beasts and Cattle, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Children of Men, bless ye the Lord: praise Him, and magnify Him for ever.

O let Israel bless the Lord: praise Him, and magnify Him for ever.

O ye Priests of the Lord, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Servants of the Lord, bless ye the Lord: praise Him, and magnify Him for ever.

O ye Spirits and Souls of the Righteous, bless ye the Lord: praise Him, and magnify Him for ever.

O ye holy and humble Men of heart, bless ye the Lord: praise Him, and magnify Him for ever.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen.

\section*{VII.}
\section*{Magnificat.}

\lettrine{M}{y} soul doth magnify the Lord: and my spirit hath rejoiced in God my Saviour.

For He hath regarded: the lowliness of His handmaiden.

For behold, from henceforth: all generations shall call me blessed.

For He that is mighty hath magnified me: and holy is His Name.

And His mercy is on them that fear Him: throughout all generations.

He hath showed strength with His arm : He hath scattered the proud in the imagination of their hearts.

He hath put down the mighty from their seat: and hath exalted the humble and meek.

He hath filled the hungry with good things: and the rich He hath sent empty away.

He remembering His mercy hath holpen His servant Israel: as He promised to our forefathers, Abraham and his seed, for ever.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen.

\section*{VIII.}
\section*{Benedictus.}

\lettrine{B}{lessed} be the Lord God of Israel: for He hath visited
and redeemed His people; 

And hath raised up a mighty salvation for us: in the house of His servant David;

As He spake by the mouth of His holy Prophets: which have been since the world began;

That we should be saved from our enemies: and from the hand of all that hate us.

To perform the mercy promised to our forefathers: and to remember His holy covenant;

To perform the oath which He sware to our forefather Abraham: that He would give us;

That we being delivered out of the hand of our enemies: might serve Him without fear;

In holiness and righteousness before Him: all the days of our life.

And thou, child, shalt be called the prophet of the Highest: for thou shalt go before the face of the Lord to prepare His ways;

To give knowledge of salvation unto His people: for the remission of their sins,

Through the tender mercy of our God: whereby the dayspring from on high hath visited us;

To give light to them that sit in darkness, and in the shadow of death: and to guide our feet into the way of peace.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen.

\section*{IX.}
\section*{Nunc Dimittis.}

\lettrine{L}{ord,} now lettest thou Thy servant depart in peace: according to Thy word.

For mine eyes have seen: Thy salvation,

Which Thou hast prepared: before the face of all people;

To be a light to lighten the Gentiles: and to be the glory of Thy people Israel.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen.

\section*{X.}
\section*{Cantate Domino.}

\lettrine{O}{ sing} unto the Lord a new song: for He hath done marvellous things.

With His own right hand, and with His holy arm: hath He gotten Himself the victory.

The Lord declared His salvation: His righteousness hath He openly showed in the sight of the heathen.

He hath remembered His mercy and truth toward the house of Israel: and all the ends of the world have seen the salvation of our God.

Show yourselves joyful unto the Lord, all ye lands: sing, rejoice, and give thanks.

Praise the Lord upon the harp: sing to the harp with a psalm of thanksgiving.

With trumpets also and shawms: O show yourselves joyful before the Lord, the King.

Let the sea make a noise, and all that therein is: the round world, and they that dwell therein.

Let the floods clap their hands, and let the hills be joyful together before the Lord: for He cometh to judge the earth.

With righteousness shall He judge the world: and the people with equity.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen. 

\section*{XI.}
\section*{Bonum est Confiteri.}

\lettrine{I}{t} is a good thing to give thanks unto the Lord: and to sing praises unto Thy Name, O Most Highest;

To tell of Thy loving-kindness early in the morning: and of Thy truth in the night season;

Upon an instrument of ten strings, and upon the lute: upon a loud intsrument, and upon the harp.

For Thou, Lord, hast made me glad through Thy works: and I will rejoice in giving praise for the operations of Thy hands.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen.

\section*{XII.}
\section*{Benedic, Anima mea.}

\lettrine{P}{raise} the Lord, O my soul: and all that is within me, praise His holy Name.

Praise the Lord, O my soul: and forget not all His benefits:

Who forgiveth all thy sin: and healeth all thine infirmities;

Who saveth thy life from destruction: and crowneth thee with mercy and loving-kindness.

O praise the Lord, ye angels of His, ye that excel in strength: ye that fulfil His commandment, and hearken unto the voice of His word.

O praise the Lord, all ye His hosts: ye servants of His that do His pleasure.

O speak good of the Lord, all ye works of His, in all places of His dominion: praise thou the Lord, O my soul.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen. 

\section*{XIII.}
\section*{Deus Misereatur.}

\lettrine{G}{od} be merciful unto us, and bless us: and show us the light of His countenance, and be merciful unto us;

That Thy way may be known upon earth: Thy saving health among all nations.

Let the people praise Thee, O God: yea, let all the people praise Thee.

O let the nations rejoice and be glad: for Thou shalt 
judge the folk righteously, and govern the nations upon
earth.

Let the people praise Thee, O God: yea, let all the
people praise Thee.

Then shall the earth bring forth her increase: and God, even our own God, shall give us His blessing.

God shall bless us: and all the ends of the world shall fear Him.

Glory be to the Father, and to the Son: and to the Holy Ghost;

As it was in the beginning, is now, and ever shall be: world without end. Amen.
