\P \textit{This Order may be used as a separate Service; or it may be said at the opening of Morning Service instead of the Order there appointed, down to the} Reading of the Holy Scriptures; \textit{in which case it may be preceded by a suitable Hymn.} \\

\noindent\P\textit{Let all stand while the Minister reads the} \textsc{Sentences,} \textit{the People answering him.}     

\begin{tabbing}
	\textit{Minister.} \= Blessed are the undefiled in the way: \\
\> who walk in the law of the Lord. \\
	\textit{Answer.} \> \textit{Order my steps in Thy Word:} \\
\> \textit{and let not any iniquity have dominion over me.} \\
	\textit{Minister.} \= Blessed are they that keep His testimonies: \\
\> and that seek Him with the whole heart. \\
	\textit{Answer.} \> \textit{With my whole heart I sought Thee:} \\
\> \textit{O let me not wander from Thy commandments.} \\
\end{tabbing}

{\centering \P\textit{Then the Minister shall say,} \\ Let us pray. \par}
\vspace{2ex}
\noindent\P\textit{Let the People reverently bow down while he leads them in}

\section*{The Invocation}

\lettrine{A}{lmighty} God, unto whom all hearts are open, all desires known, and from whom no secrets are hid; Cleanse the thoughts of our hearts by the inspiration of Thy Holy Spirit, that we may perfectly love Thee, and worthily magnify Thy holy Name; through Christ our Lord.
\textit{Amen.} \\

\noindent\P\textit{Then the Minister shall read} \textsc{The Ten Commandments,} \textit{and the People, still bowing down, shall, after every Commandment, ask God's mercy for their transgressions in time past, and grace to keep the Law in time to come.} \\

GOD spake all these words, saying, \par
I am the Lord thy God, which have brought thee our of the land of Egypt, out of the house of bondage. \par
Thou shalt have no other gods before Me.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Thou shalt not make unto thee any graven image, or any likeness of any thing that is in heaven above, or that is in the earth beneath, or that is in the water under the earth: thou shalt not bow down thyself to them, nor serve them: for I the Lord thy God am a jealous God, visiting the iniquity of the fathers upon the children unto the third and fourth generation of them that hate Me; and showing mercy unto thousands of them that love Me, and keep My commandments.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Thou shalt not take the Name of the Lord thy God in vain: for the Lord will not hold him guiltless that taketh His Name in vain.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Remember the Sabbath-day, to keep it holy.
Six days shalt thou labour, and do all thy work: but the seventh day is the Sabbath of the Lord thy God; in it thou shalt not do any work, thou, nor thy sou, nor thy daughter, thy man-servant, nor thy maid-servant, nor thy cattle, nor thy stranger that is within thy gates: for in six days the Lord made heaven and earth, the sea, and all that in them is, and rested the seventh day; wherefore the Lord blessed the Sabbath-day, and hallowed it.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Honour thy father and thy mother: that thy days may be long upon the land which the Lord thy God giveth thee.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Thou shalt not kill.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Thou shalt not commit adultery.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Thou shalt not steal.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Thou shalt not bear false witness against thy neighbor.

\textit{Lord, have mercy upon us, and incline our hearts to keep this law.}

Thou shalt not covet thy neighbour's house, thou shalt not covet thy neighbour's wife, nor his man-servant, nor his maid-servant, nor his ox, nor his ass, nor any thing that is thy neighbour's.

\textit{Lord, have mercy upon us, and write all these Thy laws in our hearts, we beseech Thee.} \\

{\centering \P\textit{Then the Minister shall say,} \par}
\vspace{2ex}

Hear also what our Lord Jesus Christ saith: \par
Thou shalt love the Lord thy God with all thy heart, and with all thy soul, and with all thy mind.
This is the first and great commandment.
And the second is like unto it; Thou shalt love thy neighbour as thyself.
On these two commandments hang all the Law and the Prophets. \\

\noindent\P\textit{After a short pause let the Minister continue in Prayer, using, if he will, the following, or other fitting words.} \\

\noindent\lettrine{W}{e} confess to Thee, Almighty God, Father, Son, and Holy Ghost, that we have grievously sinned in thought, word, and deed.
Make us truly contrite.
Fill us with holy fear, and give us grace to amend our lives according to Thy Word, for the glory of Thy holy Name; through Jesus Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{A}{lmighty} God, our heavenly Father, who of His great mercy hath promised forgiveness of sins to all them that with hearty repentance and true faith turn to Him; Have mercy upon you; pardon and deliver you from all your sins; confirm and strengthen you in all goodness; and bring you to everlasting life; through Jesus Christ our Lord. 
\textit{Amen.} \\

\noindent\lettrine{N}{ow} unto Him that is able to do exceeding abundantly above all that we ask or think, according to the power that worketh in us; unto Him be glory and dominion in the Church by Christ Jesus, throughout all ages world without end.
\textit{Amen.}
