\noindent\P \textit{Let a hymn be sung, all the People standing, and then the Minister read one or more of the following} \textsc{sentences.} \\

\lettrine{G}{race} be unto you, and peace, from God our Father, and from the Lord Jesus Christ
\textit{(Psalm 124:8, 145:18-19)} \\

Thus saith the high and lofty One that inhabiteth eternity, whose name is Holy; I dwell in the high and holy place, with him also that is of a contrite and humble spirit, to revive the spirit of the humble, and to revive the heart of the contrite ones.
\textit{(1 Corinthians 1:3)} \\

The hour cometh, and now is, when the true worshippers shall worship the Father in spirit and in truth: for the Father seeketh such to worship Him.
God is a Spirit: and they that worship Him must worship Him in spirit and in truth.
\textit{(John 4:23-24)} \\

Let my prayer be set forth before Thee as incense; and the lifting up of my hands as the evening sacrifice.
\textit{(Psalm 141:2)} \\

O worship the Lord in the beauty of holiness: fear before Him, all the earth.
\textit{(Psalm 96:9)} \\

Let the words of my mouth, and the meditation of my heart, be acceptable in Thy sight, O Lord, my strength and my redeemer.
\textit{(Psalm 19:14)}

Ask, and it shall be given you; seek, and ye shall find; knock, and it shall be opened unto you: for every one that asketh receiveth; and he that seeketh findeth; and to him that knocketh it shall be opened.
\textit{(Matthew 7:7-8)}

The Lord is good unto them that wait for Him, to the soul that seeketh Him.
\textit{(Lamentations 3:25)}

And the Spirit and the bride say, Come.
And let him that heareth say, Come.
And let him that is athirst come.
And whosoever will, let him take the water of life freely.
\textit{(Revelation 22:17)}

I will arise and go to my father, and will say unto him, Father, I have sinned against heaven and before thee, and am no more worthy to be called thy son.
\textit{(Luke 15:18-19)}

\begin{center}
\P \textit{Then shall the Minister say,} \\
\vspace{1ex}
Let us pray. \\
\vspace{1ex}
\end{center}
\P \textit{Let the People reverently bow down while the Minister leads them in the} \textsc{Invocation} \textit{and} \textsc{Confession,} \textit{using if he will one of the following Prayers:} \\

\section*{The Invocation and Confession}

\lettrine{O}{ God,} the Father of lights, with whom is no variableness nor shadow of turning; We beseech Thee to look in mercy upon us, Thy sinful and wayward children: and so direct the eyes of our faith unto Thee, that at all times we may receive a heavenly illumination, through Thy Word and Spirit; and walk securely, in confidence and peace, amid the shadows of this moral life.
And more especially at this hour of evening sacrifice, bestow upon us the pardon of our sins, and such a vision of the truth as it is in Jesus, that the darkness of evil may be driven from our hearts, and we may render unto Thee songs of praise; through Jesus Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{E}{ternal} God, in whom we live and move and have our being, whose face is hidden from us by our sins, and whose mercy we forget in the blindness of our hearts; Cleanse us, we beseech Thee, from all the defilements of this day, and deliver us from all proud thoughts and vain desires; that with lowliness and meekness we may draw near to Thee in prayer, confessing our sins, confiding in Thy grace, and finding in Thee our refuge and our strength, our hope and our salvation; through Jesus Christ Thy Son.
\textit{Amen.} \\

\noindent\lettrine{A}{lmighty} and most merciful God, who hast appointed our portion of labour, that we may serve Thee while it is day; and by whose ordinance the weariness of night cometh, that we may seek our rest in Thee; We beseech Thee now to lead and draw our hearts unto Thy dear Son, that, confessing our sin and weakness, we may receive of Him the grace promised unto the heavy-laden; and, being forgiven by His mercy, comforted by His Word, refreshed by His Spirit, and lifted up by His fellowship, we may find in this hour of worship a blessing for our souls; through Jesus Christour Lord.
\textit{Amen.} \\

\noindent\lettrine{O}{ God,} Light of the hearts that see Thee, and Life of the souls that love Thee, and Strength of the thoughts that seek Thee; from whom to be turned away is to fall, to whom to be turned is to rise, and in whome to abide is to stand fast for ever; Grant us now Thy forgiveness and blessing, as we are here assembled to offer up our confession and supplications; and though we are unworthy to approach Thee, or to ask anything of Thee at all, vouchsafe to hear and to answer us, for the sake of our great High Priest and Advocate, Jesus Christ, our Lord.
\textit{Amen.} \\

\noindent\P \textit{The Prayer may close with these Petitions of} \textsc{Holy Scripture,} \textit{to be said responsively by the Minister and People, still bowing down.} \\

Create in us a clean heart, O God: \par
\textit{And renew a right spirit within us.} \par
Cast us not away from Thy presence: \par
\textit{And take not Thy Holy Spirit from us.} \par
Restore unto us the joy of Thy salvation: \par
\textit{And uphold us with Thy free Spirit.} \par
O Lord, open Thou our lips: \par
\textit{And our mouth shall show forth Thy praise. Amen.}

\section*{The Psalter}

\P \textit{Then let a portion of the} \textsc{Psalter} \textit{be chanted, or read responsively by the Minister and the People, all standing, and at the end may be said or sung,} \\

Glory be to the Father, and to the Son, and to the Holy Ghost; \par
As it was in the beginning, is now, and ever shall be: world without end. Amen. \par
\vspace{1ex}
{\centering \P \textit{Or else, the} Gloria in Excelsis \textit{as follows:} \par}
\vspace{1ex}
\lettrine{G}{lory} be to God on high; and on earth peace, good will towards men. \par
We praise Thee, we bless Thee, we worship Thee: we glorify Thee, we give thanks to Thee for Thy great glory. \par
O Lord God, heavenly King: God the Father Almighty. \par
O Lord, the only-begotten Son, Jesus Christ: O Lord God, Lamb of God, Son of the Father, \par
That takest away the sins of the world: have mercy on us. \par
Thou that takest away the sins of the world: receive our prayer. \par
Thou that sittest at the right hand of God the Father: have mercy upon us. \par
For Thou only art holy: Thou only art the Lord. \par
Thou only, O Christ, with the Holy Ghost: art most high in the glory of God the Father.
Amen. \\

\noindent\P \textit{Note that, if any church so desire, Hymn may be sung in place of the} \textsc{Psalter.}

\section*{The Public Reading of the Holy Scriptures}

\P \textit{The People being seated shall attend devoutly to the Minister as he reads clearly and distinctly from the} Word of God. \textit{Before the reading let the Minister say,} Hear the Holy Scripture as it is written in such a chapter of such a book: \textit{and after the reading he shall say,} The Lord bless to us the reading of His Holy Word. \\

\noindent\P \textit{After the reading of Scripture, an} Anthem \textit{or} Hymn \textit{may be sung.} \\

{\centering \P \textit{Then shall the Minister say,} \\ Let us pray. \par}
\vspace{1ex}
\noindent\P \textit{And the People, reverently bowing down, shall follow in thir hearts}

\section*{The General Prayer}

\P \textit{The Minister, leading the People in their Common Prayers, shall offer unto God such} Adorations \textit{and} Thanksgivings; \textit{such} Intercessions \textit{for the Church, for the State, and for all men, especially for those who are out of Christ and those who are in any peril or distress; and such} Supplications \textit{for enlightenment, protection, and guidance; as he may think fitting for this Service. And if he will, he may use any of the Prayers given in this Book $($under the title of} \textsc{Treasury of Prayers),} \textit{or those here following:}
\vspace{1ex}
\noindent\lettrine{O}{ God,} in glory exalted, and in mercy ever-blessed: We magnify Thee, we praise Thee, we give thanks unto Thee for Thy bountiful providence, for all the blessings of this present life, and all the hopes of a better life to come. Let the memory of Thy goodness, we beseech Thee, fill our hearts with joy an thankfulness; and let no unworthiness of ours provoke Thee to withold from us any needed good, seeing that all Thy blessings come not by our desert, but only through the merit and mediation of Jesus Christ our Lord. \textit{Amen.} \\

\noindent\lettrine{O}{ Lord} of heaven and earth, who hast promised to reveal Thy glory by Jesus Christ among all nations; Remember, we beseech Thee, Thy holy Church throughout all the world. Unite all who profess and call themselves Christians in the bond of a living faith as the body of Christ, and so replenish them and us with the grace of Thy Holy Spirit, that we may bring forth abundantly the fruits of peace and good works, and may turn many to righteousness through the preaching of the Gospel. And grant that, having persevered in the way of godliness to the end, we may, with prophets, apostles, martyrs, confessors, and saints of all ages, come into full communion with Thee, and with one another, in Thine eternal and glorious kingdom; through our Lord and Saviour Jesus Christ. \textit{Amen.} \\

\noindent\lettrine{A}{lmighty} God, who hast heard the prayer of our fathers, and established our Nation in freedom according to the people's will; We implore Thy blessing on the Republic; that Thou wouldst grant us peaceful times and fruitful seasons; that Thou wouldst bless our homes, prosper our industries, and defend us from our enemies; that Thou woulst govern and protect Thy servant the President of the United States, and all to whom authority is given; the Governor of the State, and all law-makers and judges: that Thou wouldst unite the hearts of the people to dwell together in concerd: and that Thou wouldst enrich our land with liberty and order, godliness and power; for the good of the world and the glory of Thy Name; through Jesus Christ our Lord. \textit{Amen.} \\

\noindent\lettrine{O}{ God,} Creator and Preserver of all mankind, we implore Thy mercy in behalf of all classes and conditions of men; that it may please Thee to visit them with Thy help, according to their manifold necessities.
Have compassion upon all who are out of Christ, and draw them unto Him.
Show Thy pity upon all prisoners and captives; upon all sick and dying persons; and upon all who are poor, desolate, or afflicted.
Enable them to look unto Thee, O most merciful Father, and to find Thee a present Saviour in their time of trouble.
And let it please Thee to deliver them, and raise them up in due time, diving them patience under all their sufferings, the rich comfort of Thy grace on earth, and eternal rest with Thee in heaven; through our Lord Jesus Christ. \textit{Amen.} \\

\noindent\lettrine{O}{ Almighty} Lord, and everlasting God, vouchsafe, we beseech Thee, to direct, sanctify, and govern, both our hearts and bodies in the ways of Thy laws, and in the works of Thy commandments; that through Thy most mighty protection, both here and ever, we may be preserved in body and soul; through our Lord and Saviour Jesus Christ. \textit{Amen.} \\

\noindent\lettrine{L}{ighten} our darkness, we beseech Thee, O Lord; and by Thy great mercy defend us from all perils and dangers of this night; for the love of Thy only son, our Saviour, Jesus Christ. \textit{Amen.} \\

{\centering \textit{And the Prayer may close with the following} \textsc{Ascription:} \par}
\vspace{1ex}
\noindent\lettrine{N}{ow} unto Him that is able to keep you from falling, and to present you faultless before the presence of His glory with exceeding joy; to the only wise God our Savior, be glory and majesty, dominion and power, both now and ever. \textit{Amen.}

\section*{The Offering}

\P \textit{Let the Minister, having made such} \textsc{Announcements} \textit{as are needful and fitting, then say,} Let us make our Offering to Almighty God for (naming the cause).
\textit{If the choir sing a} Canticle \textit{or} Anthem \textit{it should be one proper for the occasion. When the gifts are brought to the Table, the Minister shall dedicate them to God with a brief Prayer for His blessing; the church-officers who have gathered the gifts standing, and the congregation bowing down.} \\

\noindent\P \textit{On special occasions the Offering may be made after the Sermon.}

\section*{A Prayer of Dedication}

\lettrine{A}{ll} gracious God, who of Thine infinite love didst give Thine only-begotten Son, Jesus Christ, to die for our sins and rise again for our justification, and hast made us partakers of the divine nature through the gift of the Holy Spirit; Accept the Offering which we now present unto Thee: and grant that our bodies, souls, and spirits may be unto Thee a living sacrifice, holy and well-pleasing in Thy sight; and that going forth in Thy strength, we may be able to truly serve Thee, and in all things to obey Thy will; through Jesus Christ our Lord. \textit{Amen.} \\

{\centering\P \textit{Then let the People stand up and sing }\par}

\section*{A Hymn}

\P \textit{Then the Minister, taking his text from the} \textsc{Word of God,} \textit{and remembering that it is his office to instruct men in divine Truth, to hold forth Christ crucified as their Saviour, and to incite them to Christian faith and duty, shall preach}

\section*{The Sermon}

{\centering \P \textit{The Sermon being ended, let the People stand up and sing}\par}

\section*{A Hymn}

\begin{center}
\P \textit{Then shall the Minister say,} \\
\vspace{1ex}
Let us pray. \\
\vspace{1ex}
\end{center}
\P \textit{Let the People reverently bow down while the Minister leads them in the Prayer, using if he so desire one of the following as, ending with the} \textsc{Lord's Prayer:}

\section*{The Closing Prayer}

\lettrine{G}{rant,} we beseech Thee, Almighty God, that the words, which we have heard this day with our outward ears, may through Thy grace be so grafted inwardly in our hearts that they may bring forth in us the fruit of good living to the honour and praise of Thy Name; through Jesus Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{L}{et} Thy Gospel, O Lord, come unto us not in word only but in power, and in much assurance, and in the Holy Ghost, that we may be guided into all truth, and strengthened unto all obedience and enduring of Thy will with joyfulness; that, abounding in the work of faith, and the labour of love, and the patience of hope, we may finally be made partakers of the inheritance of the saints in light; through Jesus Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{O}{ Lord} Jesus Christ, who hast died for us, that whether we wake or sleep, we should live together with Thee; Be Thou our strength every morning, and our rest when the shadows of the evening are stretched out, O Jesus Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{O}{ God,} from whom all holy desires, all good counsels, and all just works do proceed; Give unto Thy servants that peace which teh world cannot give; that both our hearts may be set to obey Thy commandments, and also that by Thee, we, being defended from the fear of our enemies, may pass our time in rest and quietness; through the merits of Jesus Christ our Saviour.
\textit{Amen.} \\

\noindent\lettrine{E}{ternal} and ever-blessed God, who art the Author of our life, and the End of our pilgrimage; We beseech Thee so to guide us by Thy Word and Spirit, amid all perils and temptations, that we may not wander from Thy way, nor stumble upon the dark mountains; but may finish our course in safety, and come to our eternal rest in Thee; through the saving grace of our Lord Jesus Christ.
\textit{Amen.} \\

\noindent\lettrine{O}{ Lord} God, the Light of the faithful, the Stregnth of those who labour, and the Repose of the blessed dead; We bless Thee for all Thy saints who have witnessed in their lives a good confession, and especially for those dear unto us who have fallen asleep in Jesus.
Grant us grace, O Lord, so to follow their good example, that we may be one with them in spirit, and finally share in their eternal rest; through Jesus Christ our Lord.
\textit{Amen.}

\section*{The Lord's Prayer}

{\centering \textit{To be said by Minister and People} \par}
\vspace{1ex}

\lettrine{O}{ur} Father which art in heaven, Hallowed be Thy Name.
Thy kingdom come.
Thy will be done in earth, As it is in heaven.
Give us this day our daily bread.
And forgive us our debts, As we forgive our debtors.
And lead us not into temptation, But deliver us from evil:
For Thine is the kingdom, and the power, and the glory, for ever.
Amen.

\noindent\P \textit{The People remaining in the posture of prayer, the Minister shall pronounce}

\section*{The Benediction}

\lettrine{T}{he} grace of the Lord Jesus Christ, and the love of God, and the communion of the Holy Ghost, be with you all.
\textit{Amen.} \\

{\centering \P \textit{Or this:} \par}
\vspace{1ex}
\noindent\lettrine{T}{he} peace of God, which passeth all understanding, keep your hearts and minds in the knowledge and love of God, and of His Son Jesus Christ our Lord; and the blessing of God Almight, the Father, the Son, and the Holy Ghost, be amongst you, and remain with you always.
\textit{Amen.} \\

\noindent\P \textit{After the Benediction it is fitting that the Minister and People remain in silent prayer, beseeching God that none may leave His House without a blessing.} \\

\noindent\P \textit{Note that the last Hymn may be sung after the Prayer if such be the wish and usage of any church.}
