\section*{Morning}

\subsection*{Sunday.}

\lettrine{G}{lory} be to Thee, O God; Giver of the morning light,
who hast raised our Lord Jesus from the dead, on this
first day of the week, that we might rejoice in it and keep
it holy, a Sabbath of the heart.

Cleanse us now, we implore Thee, from all our sin, and
bathe us with the dew of Thy divine forgiveness, that we,
being renewed in spirit, may enter gladly into the pure
worship of this day, and serve Thee with heavenly meditation and holy music, with faithful prayer and thankful
praise, with words of love and works of mercy, with joy in
Thy creation and perfect peace in Thee, according to the
teaching and the example of Thy Son, our living Saviour
Jesus Christ.
\textit{Amen.} \\

\lettrine{A}{s} the hart panteth after the water-brooks, O God, our
souls do thirst after Thee, that we may see Thy power
and Thy glory, as we have seen them in the sanctuary, and
be satisfied with the goodness of Thy House. Lead us and
guide us unto Thy holy hill, and bring us together with
sweet converse to the place of prayer, to hear Thy Word of
Truth in the spirit, to offer the sacrifices of joy with Thy
people, and to make melody in our hearts with the songs
of Zion. Prepare us, we beseech Thee, for a true entrance
into the secret of Thy tabernacle; and bless Thy churches
everywhere this day with the clear shining of Thy Presence; that the Holy Spirit may descend on many hearts,
and multitudes may be brought from the kingdom of Satan
into the kingdom of Thy dear Son Jesus Christ.
\textit{Amen.} \\

\lettrine{A}{lmighty} God, we praise Thee for the mercies which
Thou hast bestowed upon us as a household, and we
beseech Thee to bless all the families of earth with a Father’s blessing. Look mercifully upon the solitary and the
lonely, the weary and the heavy-laden, and grant them rest
unto their souls. Pity and relieve the sorrows of all mankind. Shed abroad the holy influence of the Sabbath
throughout our land, and keep our whole country, with
those who are chosen to govern it, in the way of righteousness and peace. Finally we commend to Thy fatherly
goodness all who are near and dear to us, wherever they
may be to-day, praying Thee to watch over them, to provide for them, to bless them in body and soul, and at last
to bring them and us into the perfect and eternal joy of
heaven; through Jesus Christ our Lord.
\textit{Amen.} \\ \\

\noindent\P\textit{Here any special prayer or brief petition, suited to the need of the
household, to any particular occasion, or to the season of the
year, may be added; and let all present join their voices and
hearts in}

\subsection*{The Lord's Prayer.}

\subsection*{Monday.}

\lettrine{O}{ God,} our Father, of whom the whole family in heaven
and on earth is named; Bestow upon our household, at
the beginning of this day, that grace which shall keep us
in the fellowship of the Christian way: and grant unto
each one of us that heavenly guidance and control, in all
our labours, pleasures, and trials, which shall maintain our
hearts in peace with one another and with Thee. Graciously help and prosper us in the doing of our various
duties, with a willing and a cheerful mind; and defend us
all, by Thine almighty power, both from inward evil and
from outward harm; so that, when the day is ended, it may
not leave us in sorrow, strife, or shame, but in true unity
and thankful rest, through Thy merciful favour and Thy
forgiving love, in Christ Jesus our Lord.
\textit{Amen.} \\

\lettrine{A}{lmighty} God, the Fountain of all wisdom, who
knowest our necessities before we ask, and our ignorance in asking ; We beseech Thee to have compassion upon
our infirmities; and those things which for our unworthiness we dare not, and for our blindness we cannot, ask,
vouchsafe to give us in the fulness of Thy love and grace, 
which Thou hast made known to us; through Jesus Christ
our Lord.
\textit{Amen.} \\

\lettrine{L}{ift} upon us the light of Thy countenance, O God, that
we may rejoice and be glad in Thee; and send into our
souls the purifying gift of Thy pardon, that our sins may
be utterly removed from us, and we may go forth with a
clean spirit, a joyful courage, and strength sufficient for
our needs, to meet whatever thou hast appointed for us
during this day. And grant, O most merciful Lord, that
we may neither forget the precepts and the promises of Thy
holy Word, nor depart in thought, or word, or deed from
the obedient faith of Thy true children in Jesus Christ.
\textit{Amen.} \\ \\

\noindent\P\textit{Here any special prayer or brief petition, suited to the need of the
household, to any particular occasion, or to the season of the
year, may be added; and let all present join their voices and
hearts in}

\subsection*{The Lord's Prayer.}

\subsection*{Tuesday.} 

\lettrine{O}{ Thou,} who art the true Sun of the world, evermore rising, and never going down; who, by Thy most wholesome appearing and light dost nourish, and make joyful all
things, as well that are in heaven, as also that are on earth;
We beseech Thee mercifully and favourably to shine into
our hearts, that the night and darkness of sin, and the
mists of error on every side, being driven away, Thou
brightly shining within our hearts, we may all our life
long go without any stumbling or offense, and may walk
as in the daytime, being pure and clean from the works
of darkness, and abounding in all good works which Thou
hast prepared for us to walk in.
\textit{Amen.} \\

\lettrine{A}{lmighty} God, who alone gavest us the breath of life,
and alone canst keep alive in us the breathing of holy
desires; We beseech Thee for Thy compassion's sake to
sanctify all our thoughts and endeavours, that we may
neither begin any action without a pure intention, nor continue it without Thy blessing; and grant that, having the
eyes of our understanding purged to behold things invisible and unseen, we may in heart be inspired with Thy
wisdom, and in work be upheld by Thy strength, and in
the end be accepted of Thee, as Thy faithful servants,
having done all things to Thy glory, and thereby to our
endless peace. Grant this prayer, O Lord.
\textit{Amen.} \\

\lettrine{O}{ God,} most merciful, who healest those that are broken
in heart, and turnest the sadness of the sorrowful to
joy; Let Thy Fatherly goodness be upon all that Thou hast
made. Especially we beseech Thee to remember in pity
such as are this day destitute, homeless, or forgotten of their
fellow-men. Bless the congregation of the poor. Uplift
those who are cast down, mightily befriend innocent sufferers, and sanctify to them the endurance of their wrongs.
Cheer with hope all discouraged and unhappy people, and
by Thy heavenly grace preserve from falling those whose
penury tempteth them to sin. Though they be troubled
on every side, suffer them not to be distressed; though
they be perplexed, save them from despair. Grant this,
O Lord, for the love of Him who for our sakes became
poor, Thy Son, our Saviour Jesus Christ.
\textit{Amen.} \\ \\

\noindent\P\textit{Here any special prayer or brief petition, suited to the need of the
household, to any particular occasion, or to the season of the
year, may be added; and let all present join their voices and
hearts in}

\subsection*{The Lord's Prayer.}

\subsection*{Wednesday.}

\lettrine{A}{lmighty} and most merciful Father, in whom we
live and move and have our being, to whose tender
compassion we owe our safety in days past, together with
all the comforts of this present life, and the hopes of that
which is to come; We praise Thee, O God, our exceeding
Joy, who daily pourest Thy benefits upon us. Grant, we
beseech Thee, that Jesus our Lord, the Hope of glory, may
be formed in us, in all humility, meekness, patience, contentedness, and absolute surrender of our souls and bodies
to Thy holy will and pleasure. Leave us not, nor forsake
us, O Father, but conduct us safe through all changes of
our condition here, in an unchangeable love to Thee, and in
holy tranquillity of mind in Thy love to us, till we come to
dwell with Thee, and rejoice in Thee for ever.
\textit{Amen.} \\

\lettrine{G}{rant,} O Lord, that this day which Thou hast given
unto us in mercy, may be returned unto Thee in service: As Thou hast guarded us during the helpless hours
of sleep, so do Thou guide us during the appointed hours
of labour; that all our tasks may be gladly and faithfully
performed, as in Thy sight; that our burdens may not be
too heavy for us, because Thine aid and comfort are with
us continually; and that in nothing may we displease Thee,
or injure one another. But if in anything we fail or come
short, through ignorance or weakness, O God, let Thy
fatherly wisdom correct us, and Thine infinite mercy forgive us, and Thy divine love amend our fault; through
Jesus Christ our Saviour.
\textit{Amen.} \\ \\

\noindent\P\textit{Here any special prayer or brief petition, suited to the need of the household, to any particular occasion, or to the season of the
year, may be added; and let all present join their voices and
hearts in}

\subsection*{The Lord's Prayer.}

\subsection*{Thursday.}

\lettrine{O}{ Lord,} lift up the light of Thy countenance upon us:
let Thy peace rule in our hearts; and may it be our
strength, and our song in the house of our pilgrimage.
We commit ourselves to Thy care and keeping this day;
let Thy grace be mighty in us, and sufficient for us, and
let it work in us both to will and to do of Thine own
good pleasure. Keep us from sin; give us the rule over
our own spirits; and keep us from speaking unadvisedly
with our lips. May we live together in peace and holy love,
and do Thou command Thy blessing upon us, even life for
evermore. Prepare us for all the events of the day; for
we know not what a day may bring forth. Give us grace
to deny ourselves, to take up our cross daily, and to follow
in the steps of our Lord and Master.
\textit{Amen.} \\

\lettrine{O}{ Thou} who dwellest in heaven, mercifully regard all
Thy sorrowful and afflicted children upon earth, we
beseech Thee. Draw near to them with the comfort of
Thy love, and sustain them by the right hand of Thy
power. Grant us a heart to sympathize with them in
their distress, and give us both the opportunity and the
will to help those who are in any trouble, for Jesus Christ’s
sake.
\textit{Amen.} \\

\lettrine{G}{od,} the Protector of all that trust in Thee, without
whom nothing is strong, nothing is holy; Increase and
multiply upon us Thy mercy, that, Thou being our ruler
and guide, we may so pass through things temporal, that
we may finally lose not the things eternal. Grant this, O
Lord, most merciful, for the sake of Thy dear Son, our
Saviour.
\textit{Amen.} \\ \\

\noindent\P\textit{Here any special prayer or brief petition, suited to the need of the household, to any particular occasion, or to the season of the
year, may be added; and let all present join their voices and
hearts in}

\subsection*{The Lord's Prayer.}

\subsection*{Friday.} 

\lettrine{W}{e} praise Thee, O God, with the morning light, and in
the brightness of a new day we bless Thy holy Name.
For all Thou hast bestowed upon us with the gift of life,
making us in Thine own image, and granting us to share
as children in Thy knowledge and Thy love, in Thy work
and Tny joy; we thank Thee, heavenly Father. For all
good things in the world, for food and raiment, for home
and friendship, for useful tasks and pure pleasures; we
thank Thee, heavenly Father. For all spiritual blessings,
for Thy holy Word, for the Christian fellowship, for the good
example and blessed memory of Thy saints, for the secret
influence of Thy Spirit; we thank Thee, heavenly Father.
And above all we praise and bless Thee for the life and
death of Thy dear Son, our Saviour Jesus Christ.
\textit{Amen.} \\

\lettrine{O}{ Lord,} grant that our hearts may be truly cleansed,
and filled with Thy Holy Spirit, and that we may arise
to serve Thee, in entire confidence and submission to Thy
will, ready to do and to endure whatsoever Thou hast appointed for us. Let us live for the day, not overcharged
with worldly cares, but feeling that our treasure is not
here, and desiring truly to be joined to Thee in Thy heavenly kingdom, and to those who are already gone to Thee.
O Lord, save us from sin, and guide us with Thy Spirit,
and keep us in faithful obedience to Thee; through Jesus
Christ our Lord.
\textit{Amen.} \\ \\

\noindent\P\textit{Here any special prayer or brief petition, suited to the need of the household, to any particular occasion, or to the season of the
year, may be added; and let all present join their voices and
hearts in}

\subsection*{The Lord's Prayer.}

\subsection*{Saturday.}

\lettrine{A}{lmighty} God, our Father and Preserver; We give
Thee thanks that of Thy goodness Thou hast watched
over us the past night, and brought us to a new day: and we
beseech Thee to strengthen and guard us by Thy Spirit, that
we may spend it wholly in Thy service and to Thy glory,
looking for all prosperity to Thy blessing, and seeking
only those things which are well-pleasing in Thy sight.
Enable us, O Lord, while we labour for the life that now
is, ever to have regard unto that heavenly life which Thou
hast promised Thy children. Defend us in soul and body
from all harm. And seeing it is a small thing to have begun well, except we also persevere, take us, O Lord, into
Thy good keeping this day and all our days: continue and
increase Thy grace within us, until we shall be perfectly
united in the glory of Thy Son. Show Thy loving-kindness
unto all men and women and little children, according to
the need of every living soul, especially unto those whom
we love, and those who are in any kind of trouble or distress, whom we now remember silently before Thee:
[\textit{here let there be a moment of prayer in silence:}]
Protect our country, and prosper Thy Church: Bless all who do good in the
world, and restrain and convert all who do evil. And finally,
be pleased to cast out of Thy remembrance all our past
offenses, forgiving them in Thy boundless mercy and purifying our hearts, that we may lead a better life; through
Jesus Christ our Lord.
\textit{Amen.} \\ \\

\noindent\P\textit{Here any special prayer or brief petition, suited to the need of the household, to any particular occasion, or to the season of the
year, may be added; and let all present join their voices and
hearts in}

\subsection*{The Lord's Prayer.}

\subsection*{For the Sick.}

\lettrine{O}{ Thou} who hearest prayer, we pray Thee to be very
kind and merciful to Thy child ---, whose body
suffers in pain and weakness, [and whose life, dear to us, is
in danger.] Grant unto \textit{him} patience and tranquillity of
mind; peace, purity, and courage of soul; the strong will
to live if it be Thy will; and a heart ready to trust Thee
waking or sleeping. Bless all the means used for \textit{his} recovery, and all who minister to \textit{him} in his suffering [and
peril.] Make Thou \textit{his} bed in \textit{his} sickness, and comfort
\textit{him} as a mother comforteth her child. Restore \textit{him} speedily to health, if it please Thee, but above all things grant
\textit{him} that which Thou knowest to be best for \textit{him,} and keep
\textit{him} Thine for evermore; through Jesus Christ our Saviour.
\textit{Amen.} \\

\subsection*{For the Absent.} 

\lettrine{A}{lmighty} God, who art not far from any one of us;
We commend into Thy fatherly care and keeping ---,
to whom our hearts go out in absence. Let these our loving thoughts come up before Thee as prayers and supplications; defend our beloved from all danger and harm, in
body and in soul; enrich \textit{him} with all blessings both for
this life and for that which is to come; and grant that we
may soon meet together, with joy and not with grief, to
thank Thee for all Thy mercies, in Christ Jesus our Lord.
\textit{Amen.} \\

\subsection*{For Departing Friends and Travellers.}

\lettrine{M}{ost} merciful Father, we beseech Thee to protect and prosper --- on \textit{his} intended journey.
May the Angel of Thy Presence be with \textit{him} wherever \textit{he} may go, and may all \textit{his} steps be ordered of Thee in wisdom and love;
so that \textit{he} shall travel with Thee as \textit{his} guardian and \textit{his} guide, and arrive in safety at \textit{his} desired haven.
O Lord, bless \textit{his} going-out and \textit{his} coming-in, from this time forth and even for evermore.
\textit{Amen.} \\

\subsection*{For a Family in Time of Distress.}

\lettrine{G}{od,} most wise and loving and faithful Redeemer,
Thou hast permitted us to come into this present trial,
[\textit{here the affliction may be named or silently remembered,}]
in order that we may learn obedience by the things that we
suffer, and turn to Thee, our Helper in the time of trouble.
Grant, therefore, that there may be no bitterness in our
sorrow, no despair in our submission, and no doubt of Thee
in our perplexity of heart. But do Thou teach us to face
our trial manfully, and cause even the dark things of life
to work together for our good, and bring us speedily out
of our distress, that we may praise Thee with a joyful
heart, in Christ Jesus our Lord.
\textit{Amen.} \\

\subsection*{Brief Petitions} 

\lettrine{G}{od,} who hast taught us to keep all Thy heavenly
commandments by loving Thee and our neighbour;
Grant us the spirit of peace and grace, that we may be
both devoted to Thee with our whole heart, and united to
each other with a pure will; through Jesus Christ our
Lord.
\textit{Amen.} \\

\lettrine{H}{ear} our prayers, O Lord, and consider our desires.
Give unto us true humility, a meek and quiet spirit,
a loving and a friendly, a holy and a useful manner of life;
bearing the burdens of our neighbours, denying ourselves,
and studying to benefit others, and to please Thee in all
things. Grant us to be righteous in performing promises,
loving to our relatives, careful of our charges; to be gentle
and easy to be entreated, slow to anger, and readily prepared for every good work.
\textit{Amen.} \\

\lettrine{L}{ook} upon us, O Lord, and let all the darkness of our
souls vanish before the beams of Thy brightness. Fill
us with holy love, and open to us the treasures of Thy
wisdom. All our desire is known unto Thee: therefore
perfect what Thou hast begun, and what Thy Spirit has
awakened us to ask in prayer. We seek Thy face: turn
Thy face unto us, and show us Thy glory. Then shall our
longing be satisfied, and our peace shall be perfect.
\textit{Amen.} \\

\lettrine{G}{rant} Lord, that we may not, for one moment, admit
willingly into our souls any thought contrary to Thy love.
\textit{Amen.} \\

\lettrine{O}{ Lord,} perfect, we beseech Thee, the faith of us who
believe, and sow the good seed of faith in their hearts
who as yet lack it; that we all may look steadfastly unto
Thee, and run with patience the race that is set before us.
Give us grace to show our faith by our works; teach us to
walk by faith, having respect unto the promises: which of
Thy mercy make good to us in Thine own good time, O
our most gracious Lord God and Saviour.
\textit{Amen.} \\

\lettrine{A}{lmighty} God, who art the Giver of all wisdom; Enlighten our understandings with knowledge of right,
and govern our wills by Thy laws, that no deceit may mislead us, nor temptation corrupt us; that we may always
endeavour to do good, and to hinder evil. Amidst all the
hopes and fears of this world, take not Thy Holy Spirit
from us; but grant that our thoughts may be fixed on Thee,
and that we may finally attain everlasting happiness, for
Jesus Christ’s sake.
\textit{Amen.} \\

\lettrine{O}{ God,} who hast commanded us to be perfect, as Thou
our Father in heaven art perfect; Put into our hearts,
we pray Thee, a continual desire to obey Thy holy will.
Teach us day by day what Thou wouldest have us do, and
give us grace and power to fulfil the same. May we never,
from love of ease, decline the path which Thou pointest
out, nor, for fear of shame, turn away from it.
\textit{Amen.} \\

\lettrine{O}{ Almighty} Lord, and everlasting God, vouchsafe, we
beseech Thee, to direct, sanctify, and govern,both our
hearts and bodies in the ways of Thy laws, and in the
works of Thy commandments; that through Thy most
mighty protection, both here and ever, we may be preserved
in body and soul; through our Lord and Saviour Jesus
Christ.
\textit{Amen.} \\

\section*{Evening.}

\subsection*{A General Prayer.}

\lettrine{O}{ God} most merciful, Light eternal in the darkness shining, by whom the night of sin and the blindness of our
hearts are driven away: Since Thou hast appointed the day
for labour and the night for rest; grant unto us, we beseech Thee, that our bodies may repose in peace and quietness, that afterward they may be able to endure the toil
which Thou hast laid upon us in Thy service: Temper our
sleep that it be not disorderly, and keep us spotless both
in body and in soul, that our very rest may be to Thy
glory, renewing the strength of our hearts and our joy in
Thee: Enlighten the eyes of our understanding that we
may not sleep in death, but obtain deliverance, through
faith and hope, from all fear of this misery: Defend us
against all assaults of our enemies, and take us into Thy
holy protection. And although we have not passed this
day without greatly sinning against Thee, we beseech
Thee to hide our sins with Thy mercy, as Thou coverest
all things on earth with the darkness of the night, that
they may be blotted out from Thy remembrance, and we
may abide in Thy presence and Thy favour, both now and
for evermore. Relieve and comfort, with Thy fatherly
goodness, all who are afflicted or distressed in mind, body,
or estate: Protect and prosper, with Thine almighty power,
our country and our rulers, the whole Church of Christ on
earth, our home, and all that we hold dear and sacred: Be
pleased to guard and help those whom we silently remember before Thee:
[\textit{here let there be a moment of prayer in silence :}]
Bless us and keep us, watch over us and save us,
O God in whom we trust; through Jesus Christ our Lord.
\textit{Amen.} \\

\subsection*{Various Prayers.} 

\lettrine{A}{lmighty} God, who seest that we have no power of
ourselves to help ourselves; Keep us both outwardly
in our bodies and inwardly in our souls, that we may be
defended from all adversities which may happen to the
body, and from all evil thoughts which may assault and
hurt the soul; through Jesus Christ our Lord.
\textit{Amen.} \\

\lettrine{A}{lmighty} God, the Father of our spirits; Meet with us
at close of day, and grant unto us, Thy children, the
peace which the world cannot give. May no unhallowed
thoughts or cares disturb the quiet of this evening hour.
Deliver us from the vain things which have such power
over us. May we learn wisdom, receive strength, gain
hope, feel the influence of things unseen, and find rest in
God.
\textit{Amen.} \\

\lettrine{C}{onfirm} O Lord, we pray Thee, the hearts of Thy
children, and strengthen them with the power of Thy
grace; that they may both be devout in prayer to Thee,
and sincere in love for each other; through Jesus Christ
our Lord.
\textit{Amen.} \\

\lettrine{O}{ God,} Father of our spirits and Giver of all good; Grant
that we may live in such fellowship with Thee that
we shall grow into Thy likeness, and share Thy life. Free
us from fretting and pride, and beget within us a meek
and modest spirit. Deliver us from the bondage and bitterness of a worldly life, and lead us out into the large and
joyous liberty of Christ. May He so dwell in us that His
spirit shall become our disposition, and spring up within
us a well of water unto everlasting life. Lead us in a plain
path along life’s journey, and at last may we enter in
through the gates into the City. And this we ask in Jesus’ Name.
\textit{Amen.} \\

\lettrine{F}{ather} of our spirits, and Father of our Lord and Saviour Jesus Christ; Bind us to Thyself with cords of
faith, and love that can never be broken or strained. May
we feel the impulse of our divine childhood, and find rest in
Thee. Feed us out of Thy Word, and may it be sweet to
our souls. May prayer daily acquaint us with Thee, and
make us calm and strong. Cause the light of Thy face to
shine upon us, so that we shall ever see our path, and find
the world our Father’s home. Give us patience and peace
under every burden. May we not be anxious and troubled
over many things, but have the one thing needful and be
content. O Master, let us walk with Thee!
\textit{Amen.} \\

\lettrine{W}{e} beseech Thee, Lord, to behold us with favour, gathered together in the peace of this roof, weak men and
women subsisting under the covert of Thy patience. Be
patient still; suffer us yet a while longer;--with our broken
purposes of good, with our idle endeavours against evil,
suffer us a while longer to endure and (if it may be) help
us to do better. Bless to us our extraordinary mercies; if
the day come when these must be taken, brace us to play
the man under affliction. Be with our friends, be with
ourselves. Go with each of us to rest; if any awake, temper to them the dark hours of watching; and when the day
returns, return to us, our Sun and Comforter, and call us
up with morning faces and with morning hearts--eager
to labour--eager to be happy, if happiness shall be our
portion--and if the day be marked for sorrow, strong to
endure it.
\textit{Amen.} \\

\lettrine{O}{ Lord,} make us to love Thee, and each other in Thee,
and to meet before Thee to dwell in Thine everlasting love.
\textit{Amen.} \\

\lettrine{L}{ord,} support us all day long of this troublous life,
until the shadows lengthen and the evening comes, and
the busy world is hushed, and the fever of life is over, and
our work is done. Then in Thy mercy grant us a safe
lodging, and a holy rest, and peace at the last; through
Jesus Christ our Lord.
\textit{Amen.} \\

\lettrine{S}{end} Thy peace into our hearts, O Lord, at the evening
hour, that we may be contented with Thy mercies of
this day, and confident of Thy protection for this night;
and now, having forgiven others, even as Thou dost forgive us, may we have a pure comfort and a healthful rest
within the shelter of this home; through Jesus Christ our Saviour.
\textit{Amen.} \\

\lettrine[lines=1]{L}{ighten} our darkness, we beseech Thee, O Lord; and
by Thy great mercy defend us from all perils and dangers of this night; for the love of Thy only Son, our Saviour, Jesus Christ.
\textit{Amen.} \\

\lettrine{A}{lmighty} God, with whom do rest the spirits of just
men made perfect; we bless and praise Thy holy Name
for all Thy servants departed this life in Thy faith and
fear; and especially for those most dear to us who have
fallen asleep in Jesus. And we beseech Thee to give us
grace so to follow their good example, that we may continue united to them in fellowship of spirit, and that finally
we may be gathered together in Thy heavenly kingdom;
through Jesus Christ our Lord.
\textit{Amen.} \\

\subsection*{The Confession of Sins.} 

\lettrine{M}{ost} holy and merciful Father; We acknowledge and
confess in Thy Presence: Our sinful nature prone to
evil and slothful in good ; And all our shortcomings and
offenses against Thee. Thou alone knowest how often we
have sinned: In wandering from Thy ways; In wasting
Thy gifts; In forgetting Thy love. But Thou, O Lord,
have pity upon us; Who are ashamed and sorry for all
wherein we have displeased Thee. Teach us to hate our
errors; Cleanse us from our secret faults; And forgive
our sins; For the sake of Thy dear Son our Saviour. And
O most holy and loving Father; Send Thy purifying grace
into our hearts, we beseech Thee; That we may henceforth live in Thy light and walk in Thy ways; According
to the commandments of Jesus Christ our Lord.
\textit{Amen.} \\

\subsection*{The Lord's Prayer}

\lettrine{O}{ur} Father which art in heaven, Hallowed be Thy Name.
Thy kingdom come. Thy will be done in earth, As it
is in heaven. Give us this day our daily bread. And forgive us our debts, As we forgive our debtors. And lead
us not into temptation, But deliver us from evil: For Thine
is the kingdom, and the power, and the glory, for ever.
\textit{Amen.} \\

\section*{Forms of Grace Before Meat.} 

\lettrine{T}{he} Lord make us grateful for all His mercies, and add
His blessing, for Christ’s sake.
\textit{Amen.} \\

\lettrine{A}{lmighty} God, who providest for us, nourish our
souls with the Bread of Life in Jesus Christ.
\textit{Amen.} \\

\lettrine{B}{less} us, O Lord, in blessing Thee, as we receive Thy
gift of daily bread.
\textit{Amen.} \\

\lettrine{T}{he} Lord bless this food to our use, and us to His service.
\textit{Amen.} \\

\lettrine{L}{ord} help us to receive all good things as from Thy
hand, and to use them to Thy praise.
\textit{Amen.} \\

\lettrine{H}{eavenly} Father, make us thankful to Thee, and
mindful of others, as we receive these blessings, in
Jesus’ Name.
\textit{Amen.} \\

\lettrine{F}{ather} in heaven, sustain our bodies with this food,
our hearts with true friendship, and our souls with Thy
truth, for Christ’s sake.
\textit{Amen.} \\

\lettrine{L}{ord} Jesus, be our holy Guest,
Our morning Joy, our evening Rest;
And with our daily bread impart
Thy love and peace to every heart.
\textit{Amen.} \\
