\noindent\P\textit{Forasmuch as Marriage is a sacred relation, the ground of
human fellowship and society, and most precious to mankind;
although it be not a Sacrament nor peculiar to the Church of
Christ, it is proper that it be solemnized by a lawful Minister,
that he may give counsel from the Word of God to those entering holy wedlock, and invoke the Divine blessing upon then.} \\

\noindent\P\textit{The Persons to be married shall present themselves before the
Minister, the Woman standing at the left hand of the Man.
Then, all present reverently standing, the Minister shall say,} \\

\lettrine{D}{early} beloved, we are assembled here in the presence
of God, to join this Man and this Woman in holy Marriage; which is instituted of God, regulated by His commandments, blessed by our Lord Jesus Christ, and to be
held in honour among all men. Let us therefore reverently
remember that God has established and sanctified Marriage, for the welfare and happiness of mankind. Our Saviour has declared that a man shall forsake his father and
mother and cleave unto his wife. By His apostles, He has
instructed those who enter into this relation to cherish a
mutual esteem and love; to bear with each other’s infirmities and weaknesses; to comfort each other in sickness,
trouble, and sorrow; in honesty and industry to provide
for each other, and for their household, in temporal things;
to pray for and encourage each other in the things which
pertain to God; and to live together as the heirs of the
grace of life.

Forasmuch as these two Persons have come hither to be
made one in this holy estate, if there be any here present
who knows any just cause why they may not lawfully be
joined in Marriage, I require him now to make it known,
or ever after to hold his peace. \\

\noindent\P\textit{Then, speaking unto the Persons who are to be married, he shall say,} \\

\lettrine{I}{ charge} you both, before the great God the Searcher
of all hearts, that if either of you know any impediment,
why ye may not lawfully be joined together in Marriage,
ye do now confess it. For be ye well assured that if any
persons are joined together otherwise than as God’s Word
allows, their union is not blessed by Him. \\

{\centering\P\textit{Then, if no impediment appear, the Minister shall say,}\par}
\vspace{1ex}

{\centering Let us pray. \par}
\vspace{1ex}

\lettrine[lines=1]{A}{lmighty} and ever blessed God, whose Presence is
the happiness of every condition, and whose favour
sweetens every relation; We beseech Thee to be present
and favourable unto these Thy servants, that they may be
truly joined in the honourable estate of Marriage, in the covenant of their God. As Thou hast brought them together
by Thy providence, sanctify them by Thy Spirit, giving
them a new frame of heart fit for their new estate; and enrich them with all grace, whereby they may enjoy the
comforts, undergo the cares, endure the trials, and perform the duties of life together as becometh Christians,
under Thy heavenly guidance and protection; through our
Lord Jesus Christ.
\textit{Amen.} \\

{\centering\P\textit{Then the Minister shall say to the Man,}\par}
\vspace{1ex}

\lettrine{M}{---,} wilt thou have this Woman to be thy wife, and
wilt thou pledge thy troth to her, in all love and
honour, in all duty and service, in all faith and tenderness,
to live with her, and cherish her, according to the ordinance
of God, in the holy bond of Marriage? \\

{\centering\textit{The Man shall answer,}\par}
\vspace{1ex}

{\centering I will. \par}
\vspace{1ex}

{\centering\P\textit{Then the Minister shall say to the Woman,}\par}
\vspace{1ex}

\lettrine{N}{---,} wilt thou have this Man to be thy husband, and
wilt thou pledge thy troth to him, in all love and
honour, in all duty and service, in all faith and tenderness,
to live with him, and cherish him, according to the ordinance of God, in the holy bond of Marriage? \\

{\centering\textit{The Woman shall answer,}\par}
\vspace{1ex}

{\centering I will. \par}
\vspace{1ex}

{\centering\P\textit{Then the Minister may say,}\par}
\vspace{1ex}

\lettrine[lines=1]{W}{ho} giveth this Woman to be married to this Man? \\

\noindent\P\textit{Then the father, (or guardian or any friend,) of the Woman
shall put her right hand into the hand of the Minister, who
shall cause the Man with his right hand to take the Woman by
her right hand and to say after him as follows:} \\

\lettrine{I}{,} \textit{M.}, take thee \textit{N.}, To be my wedded wife; And I do
promise and covenant, Before God and these witnesses,
To be thy loving and faithful husband, In plenty and in
want, In joy and in sorrow, In sickness and in health, As
long as we both shall live. \\

\noindent\P\textit{Then shall they loose their hands; and the Woman with her
right hand taking the Man by his right hand, shall likewise say
after the Minister:} \\

\lettrine{I}{,} \textit{N.}, take thee \textit{M.}, To be my wedded husband; And I do
promise and covenant, Before God and these witnesses,
To be thy loving and faithtul wife, In plenty and in want,
In joy and in sorrow, In sickness and in health, As long as
we both shall live. \\

\noindent\P\textit{Then,if a Ring be provided, it shall be given to the Minister, who
shall return it to the Man, who shall then put it upon the fourth
finger of the Woman’s left hand, saying after the Minister,} \\

\lettrine{T}{his} Ring I give thee, In token and pledge, Of our constant faith, And abiding love. \\

{\centering\P\textit{Then the Minister shall say,}\par}
\vspace{1ex}

{\centering Let us pray. \par}
\vspace{1ex}

\lettrine{M}{ost} merciful and gracious God, of whom the whole
family in heaven and earth is named; Bestow upon
these Thy servants the seal of Thine approval, and Thy
fatherly benediction: granting unto them grace to fulfil,
with pure and steadfast affection, the vow and covenant
between them made. Guide them together, we beseech
Thee, in the way of righteousness and peace, that loving
and serving Thee, with one heart and mind, all the days
of their life, they may be abundantly enriched with the
tokens of Thine everlasting favour, in Jesus Christ our
Lord.
\textit{Amen.} \\

\lettrine{O}{ur} Father which art in heaven, Hallowed be Thy Name.
Thy kingdom come. Thy will be done in earth, As it
is in heaven. Give us this day our daily bread. And forgive us our debts, As we forgive our debtors. And lead
us not into temptation, But deliver us from evil: For Thine
is the kingdom, and the power, and the glory, for ever.
Amen. \\

{\centering\P\textit{Then shall the Minister say unto all who are present,}\par}
\vspace{1ex}

\lettrine{B}{y} the authority committed unto me as a Minister of the
Church of Christ, I declare that \textit{M.} and \textit{N.} are now
Husband and Wife, according to the ordinance of God, and
the law of the State: in the Name of the Father, and of the
Son, and of the Holy Ghost. Amen. \\

{\centering\P\textit{Then, causing the Husband and Wife to join their right hands,
the Minister shall say,}\par}
\vspace{1ex}

\lettrine{W}{hom} therefore God hath joined together, let no man
put asunder. \\

{\centering\P\textit{And the Minister shall pronounce this} \textsc{Blessing:}\par}
\vspace{1ex}

The Lord bless you and keep you: The Lord make His
face to shine upon you and be gracious unto you:

The Lord lift up His countenance upon you and give you
peace:

Both now and in the life everlasting. \textit{Amen.}
