\section*{The Call to Worship}
\P \textit{Let the Minister and all the People stand up and sing the following, or some other Hymn or Psalm calling to Worship.} \\

Praise God, from whom all blessings flow; \par
Praise Him, all creatures here below; \par
Praise Him above, ye heavenly host; \par
Praise Father, Son, and Holy Ghost. Amen. \\

\noindent\P \textit{Let the Minister read one of the following} \textsc{Sentences,} \textit{the People standing.}

\noindent\P \textit{If any church so desire the Service may begin with the} \textsc{Sentences.} \\

\lettrine{O}{ur} help is in the Name of the Lord, who made heaven and earth.
The Lord is nigh unto all them that call upon Him, to all that call upon Him in truth.
He will fulfil the desire of them that fear Him: He also will hear their cry, and will save them. \textit{(Psalm 124:8, 145:18-19)} \\

O come, let us worship and bow down: let us kneel before the Lord our maker.
Know ye that the Lord He is God: it is He that hath made us, and not we ourselves; we are His people, and the sheep of His pasture. \textit{(Psalm 95:6, 100:3)} \\

Seek ye the Lord while He may be found, call ye upon Him while He is near: Let the wicked forsake his way, and the unrighteous man his thoughts: and let him return unto the Lord, and He will have mercy upon; and to our God for He will abundantly pardon. \textit{(Isaiah 55:6-7)} \\

The Lord is merciful and gracious, slow to anger, and plenteous in mercy.
He hath not dealt with us after our sins; nor rewarded us according to our iniquities.
If we confess our sins, He is faithful and just to forgive us our sins, and to cleanse us from all unrighteousness. \textit{(Psalm 103:8, 10; 1 John 1:9)} \\

Seeing that we have a great High Priest, that is passed into the heavens, Jesus the Son of God: Let us therefore come boldly unto the throne of grace, that we may obtain mercy, and find grace to help in time of need. \textit{(Hebrews 4:14, 16)}

\begin{center}
\P \textit{Then shall the Minister say,} \\
\vspace{1ex}
Let us pray. \\
\vspace{1ex}
\P \textit{Let the People reverently bow down while the Minister leads them in the} \textsc{Invocation,} \textit{using if he will one of the following Prayers:} \\

\end{center}

\section*{The Invocation}

\lettrine{A}{lmighty} God, who of Thy great mercy hast gathered us into Thy visible Church; Grant that we may not swerve from the purity of Thy worship; but so honour Thee, both in spirit and in outward form, that Thy Name may be glorified in us, and we may be true members of Thine only-begotten Son, Jesus Christ our Lord. \textit{Amen.} \\

\noindent\lettrine{E}{ternal} God, our Maker and our Lord, Giver of all grace, from whom every good prayer cometh, and who pourest Thy Spirit upon all who seek Thee; Deliver us, when we draw nigh to Thee, from coldness of heart and wanderings of mind; that with steadfast thoughts and pure affections we may worship Thee in spirit and in truth; through Jesus Christ our Lord. \textit{Amen.} \\

\noindent\lettrine{L}{ord} God of heaven and earth, who hast made the Church Thy dwelling-place, and chosen it as Thy rest for ever, and hast taught us in Thy Word not to forsake the assembling of ourselves together; Regard us in Thy mercy, we beseech Thee, and send Thy Holy Spirit upon us; that our worship may prepare us both to serve Thee now, and to glorify Thee hereafter in Thine eternal kingdom; through Jesus Christ our Lord. \textit{Amen.} \\

\noindent\lettrine[lines=1]{O}{ God}, who hast promised that in all places where Thou dost record Thy Name, Thou wilt meet with Thy servants to bless them; Fulfil now Thy promise, and make us joyful in Thy house of prayer; that our worship, being offered in the Name of Thy Son and by the guidance of Thy Spirit, may be acceptable unto Thee, and profitable unto ourselves; through our only Mediator and Advocate, Jesus Christ our Lord. \textit{Amen.} \\

\noindent\lettrine{A}{lmighty} Lord and everlasting God, whom the heaven of heavens cannot contain, much less the temples which our hand have builded, but who are ever nigh unto the humble and contrite; Shed down Thy Holy Spirit, we beseech Thee, on all here assembled; that being cleansed and illumined by His grace, we may worthily show forth Thy priase, meekly learn Thy Word, render due thanks for Thy mercies, and obtain a gracious answer to our prayers; through the merits of Jesus Christ our Lord. \textit{Amen.} \\

\section*{The Confession of Sins}

{\centering \P \textit{The People may say this} \textsc{Confession} \textit{with the Minister:}\par}
\vspace{1ex}
\lettrine{M}{ost} holy and merciful Father; We acknowledge and confess in Thy Presence: Our sinful nature prone to evil and slothful in good; And all our shortcomings and offenses against Thee.
Thou alone knowest how often we have sinned: In wandering from Thy ways; In wasting Thy gifts; In forgetting Thy Love.
But Thou, O Lord, have pity upon us; Who are ashamed and sorry for all wherein we have displeased Thee.
Teach us to hate our errors; Cleanse us from our secret faults; And forgive our sins; For the sake of Thy dear Son our Saviour.
And O most holy and loving Father; Send Thy purifying grace into our hearts, we beseech Thee; That we may henceforth live in Thy light and walk in Thy ways; According to the commandments of Jesus Christ our Lord. \textit{Amen.}

\section*{The Assurance of Pardon}
{\centering\P\textit{To be said by the Minister, the People still bowing down.} \par}
\vspace{1ex}

\lettrine{A}{lmighty} God, who doth freely pardon all who repent and turn to Him; Now fulfil in every contrite heart the promise of redeeming grace; remitting all our sins, and cleansing us from an evil conscience; through the perfect sacrifice of Christ our Lord; And keep us evermore in the peace and joy of a holy life; that we may love and serve Him always; In the Name of the Father, the Son, and the Holy Ghost. \textit{Amen.} \\

{\centering \P \textit{Or this:} \par}
\vspace{1ex}

\lettrine{G}{od} so loved the world, that He gave His only-begotten Son, that whosoever believeth in Him should not perish, but have everlasting life.

Hear the gracious words of our Lord Jesus Christ unto all that truly repent and turn to Him:

Come unto me, all ye that labour and are heavy laden, and I will give you rest.

Him that cometh to Me I will no wise cast out.

The grace of the Lord Jesus Christ be with you all. \textit{Amen}

\vspace{2ex}

{\centering \P \textit{Then let the Minister and the People, standing, say,} \par}
\vspace{-2ex}
\begin{tabbing}
	\textit{Minister.} \= Now bless the Lord our God: \\
	\textit{Answer.} \> \textit{And praise His glorious Name.} \\
	\textit{Minister.} \= O give thanks unto the Lord, for He is good: \\
	\textit{Answer.} \> \textit{For His mercy endureth for ever.} \\
\end{tabbing}

\section*{The Psalter}

\P \textit{Then let a portion of the} \textsc{Psalter} \textit{be chanted, or read responsively by the Minister and the People, all standing, and at the end may be said or sung,} \\

Glory be to the Father, and to the Son, and to the Holy Ghost; \par
As it was in the beginning, is now, and ever shall be: world without end. Amen.

\section*{The Public Reading of the Holy Scriptures}

\P \textit{Let the Minister read from the} \textsc{Word of God} \textit{as it is written in the} \textsc{Old} \textit{and} \textsc{New Testaments,} \textit{clearly and distinctly, that the People may understand the meaning.
If a lesson from each Testament is read, as is most proper and profitable, that from the} \textsc{Old Testament} \textit{may be followed, in places where there are choirs, by the singing of an} \textsc{Anthem} \textit{or} \textsc{Response.} \\

\noindent\P \textit{Before each reading let the Minister say,} Hear the Holy Scripture as it is written in such a chapter of such a book: \textit{and after the reading,} The Lord bless to us the reading of His Holy Word. \\

\noindent\P \textit{If the} \textsc{Old Testament} \textit{reading be} the \textsc{Ten Commandments,} \textit{after them the Minister shall read Matthew 22:37-40, saying before he reads,} Hear also the \textsc{Summary of the Law} by our Lord Jesus Christ.

\section*{A Hymn of Praise}

\P \textit{Here let the People stand up and praise God with the spirit and with the understanding, making melody with their voices as well as their hearts, unto the Lord.
And at the close of the Hymn let them remain standing and join with the Minister in their} \textsc{Confession of Faith.}

\section*{The Creed}

\lettrine{I}{ believe} in God the Father Almighty, Maker of heaven and earth:

And in Jesus Christ His only Son, our Lord; Who was conceived by the Holy Ghost, Born of the Virgin Mary, Suffered under Pontius Pilate, Was crucified, dead, and buried; [He descended into hell;\footnote{Or, \textit{He continued in the state of the dead, and under the power of death, until the third day.}}]
The third day He rose again from the dead; He ascended into heaven, And sitteth on the right hand of God the Father Almighty; From thence He shall come to judge the quick and the dead.

I believe in the Holy Ghost; The Holy Catholic Church; The Communion of Saints; The Forgiveness of sins; The Resurrection of the body; and the Life everlasting. Amen. \\

{\centering \P \textit{Then shall the Minister say,} \\ Let us pray. \par}
\vspace{1ex}
\noindent\P \textit{And the People, reverently bowing down, shall follow in thir hearts}

\section*{The General Prayer}

\P \textit{The Minister, leading the People in their Common Prayers, shall come with a heart prepared to offer unto God--} \\

\noindent \textsc{Adorations:} \textit{for His glorious perfection, and for the revelation of Himself in His works, in His Word, and in His Son, Jesus Christ:} \\

\noindent \textsc{Thanksgivings:} \textit{for all the mercies fo every kind, general and particular, spiritual and temporal, common and special; above all, for Jesus Christ, His unspeakable gift, and the hope of eternal life through Him.} \\

\noindent \textsc{Supplications:} \textit{for the supply of all our needs temporal and spiritual, and for the aid and comfort of the Holy Ghost in all our duties and trials:} \\

\noindent \textsc{Intercessions:} \textit{for the whole world of mankind; remembering especially our country and all who are invested with civil authority; the Church Universal and that with which we are particularly connected; all missionaries and ministers of the Gospel; and all others who are seeking to do good on earth; all poor and sick and sorrowful people, (especially those for whom our prayers are asked;) all little children and the youth assembled in schools and colleges; those who are in the midst of great danger or temptation; and all who are bound to us by ties of kinship or affection:} \\

\noindent \P \textit{In any or all of these} Adorations, Thanksgivings, Supplications, \textit{and} Intercessions, \textit{the Minister, if he will, may use any of the} Prayers \textit{given in this Book, under the title of} \textsc{Treasury of Prayers.}
\textit{Or he may carefully order his thoughts and compose his spirit to utter with propriety the desires and petitions of the People, remembering what is suitable and necessary for them in their Common Worship.
At the end of the General Prayer the Minister and People shall say together the} \textsc{Lord's Prayer.}

\section*{The Lord's Prayer}

\lettrine{O}{ur} Father which art in heaven, Hallowed be Thy Name.
Thy kingdom come.
Thy will be done in earth, As it is in heaven.
Give us this day our daily bread.
And forgive us our debts, As we forgive our debtors.
And lead us not into temptation, But deliver us from evil:
For Thine is the kingdom, and the power, and the glory, for ever.
Amen.

\section*{The Offering}

\P \textit{The bringing of offerings for the service of God is to be performed as an Acts of Worship.
Let the Minister, having made such} \textsc{Announcements} \textit{as are needful and fitting, then say,} Let us make our Offering to Almighty God for (naming the cause).
\textit{If the choir sing a} Canticle \textit{or} Anthem \textit{it should be one proper for the occasion.} \\

\noindent\P \textit{When the gifts are brought to the Table, the Minister shall dedicate them to God with a brief Prayer for His blessing; the church-offices who have gathered the gifts standing, and the congregation bowing down.} \\

\noindent\P \textit{On special occasions the Offering may be made after the Sermon.}

\section*{A Prayer of Dedication}

\lettrine{O}{ God,} most merciful and gracious, of whose bounty we have all received; We beseech Thee to accept this Offering of Thy people.
Remember in Thy love those who have brought it, and those for whom it is given; and so follow it with Thy blessing that it may promote peace and good-will among men, and advance the kingdom of our Lord and Saviour Jesus Christ. \textit{Amen.} \\

{\centering\P \textit{Then let the People stand up and sing }\par}

\section*{A Hymn}

\P \textit{Then the Minister, taking his text from the} \textsc{Word of God,} \textit{and remembering that it is his office to instruct men in divine Truth, to hold forth Christ crucified as their Saviour, and to incite them to Christian faith and duty, shall preach}

\section*{The Sermon}

{\centering \P \textit{The Sermon being ended, let the People stand up and sing}\par}

\section*{A Hymn}

\begin{center}
\P \textit{Then shall the Minister say,} \\
\vspace{1ex}
Let us pray. \\
\vspace{1ex}
\end{center}
\P \textit{Let the People reverently bow down while the Minister leads them in the Prayer, using if he so desire one of the following as}

\section*{The Closing Prayer}

\lettrine{O}{ God}, the Protector of all that trust in Thee, without whom nothing is strong, nothing is holy; Increase and multiply upon us Thy mercy, that, Thou being our ruler and guide, we may so pass through things temporal, that we finally lose not the things eternal.
Grant this, O heavenly Father, for Jesus Christ's sake, our Lord.
\textit{Amen.} \\

\noindent\lettrine{O}{ Lord}, the Author of spiritual life, who hast given unto us the good seed of Thy Word; Grant that we may receive it into honest hearts; and so guard it by Thy grace from the wiles of Satan and the cares of this life, that the faith and hope and love which Thou hast begotten, may be in us the beginning of life eternal; through Jesus Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{O}{ God}, who hast sounded in our ears Thy divine and saving oracles; Enlighten the souls of us sinners to the full understanding of what has been spoken, that we may be not only hearers of spiritual words, but also doers of good works, following after faith unfeigned, blameless life, and irreproachable conduct; through Jesus Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{M}{ost} merciful God, we beseech Thee to grant unto us that we may earnestly desire, wisely search out, truly perceive, and perfectly fulfil those things which are well pleasing in Thy sight, to the praise and glory of Thy Name.
\textit{Amen.} \\

\noindent\lettrine{O}{ God,} who art the Author of peace and Lover of concord, in knowledge of whom standeth our eternal life, whose service is perfect freedom; Defend us Thy humble servants in all assaults of our enemies; that we, surely trusting in thy defense, may not fear the power of any adversaries; through the might of Jesus Christ our Lord.
\textit{Amen.} \\

\noindent\lettrine{A}{lmighty} God, who hast given us grace at this time with one accord to make our common supplications unto Thee; and dost promise that when two or three are gathered together in Thy Name Thou wilt grant their requests; Fulfil now, O Lord, the desires and petitions of Thy servants, as may be most expedient for them; granting us in this world knowledge of Thy truth, and in the age to come life everlasting.
\textit{Amen.} \\

\noindent\P \textit{The People remaining in the posture of prayer, the Minister shall pronounce}

\section*{The Benediction}

\lettrine{T}{he} grace of the Lord Jesus Christ, and the love of God, and the communion of the Holy Ghost, be with you all.
\textit{Amen.} \\

{\centering \P \textit{Or this:} \par}
\vspace{1ex}
\noindent\lettrine{T}{he} peace of God, which passeth all understanding, keep your hearts and minds in the knowledge and love of God, and of His Son Jesus Christ our Lord; and the blessing of God Almight, the Father, the Son, and the Holy Ghost, be amongst you, and remain with you always.
\textit{Amen.} \\

\noindent\P \textit{After the Benediction it is fitting that the Minister and People remain in silent prayer, beseeching God that none may leave His House without a blessing.} \\

\noindent\P \textit{Note that the last Hymn may be sung after the Prayer if such be the wish and usage of any church.}
